Centrality and Activity for Envolving Networks

### 2013-06-20 network-science/paper.tex
3

%>>>
%>>>
\title %<<< Title Region
{
	Metrics and Algorithms for Envolving Social Networks
}
\author
{
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
	\and
	Yu Yan\\
	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
	\and
	Qingyang Li\\
	\href{mailto:591527324@qq.com}{591527324@qq.com}
	\and
	Xin Xing\\
	\href{mailto:823291634@qq.com}{823291634@qq.com}
}
\date{}
%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered to be vertex while friendship is considered to be edge.
\end{abstract}

\section{Introduction}
\section{}
\section{}
\section{Conclusion}

>>>>

%>>>
%>>>
\title %<<< Title Region
{
	Metrics and Algorithms for Evolving Social Networks
}
\author
{
	Pufan He\\
	\href{mailto:hpfdf@126.com}{hpfdf@126.com}
	\and
	Yichao Zhou\\
	\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com}
	\and
	Qiwei Feng\\
	\href{mailto:gdfqw93@163.com}{gdfqw93@163.com}
	\and
	Yu Yan\\
	\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com}
	\and
	Qingyang Li\\
	\href{mailto:591527324@qq.com}{591527324@qq.com}
	\and
	Xin Xing\\
	\href{mailto:823291634@qq.com}{823291634@qq.com}
}
\date{}
%>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered to be vertex while friendship is considered to be edge. We
suppose the evolution of a social network overtime only includes bidirectional
new connections between exsisting or newly created nodes, and we assume the
graph will evolve as a typical social network. We study the centrality and
activity metrics for nodes in such graphs by regulate a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developped a practical based
framework to maintain the evolving network and the algorithm to compute our
metrics with preferable time and space consumption, including historical
queries. Finally, we put the result of experiment with a couple of authentic
data.

\textbf{Keywords.} social network, dynamic graph, centrality, activity, algorithm. 
\end{abstract}

\section{Introduction}
social network
\section{}
\section{}
\section{Conclusion}
